Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
more stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58581 72bbbca6-d526-0410-a7d9-f06f51895060

%Rules: m\"{a} -> min\"{a}, oon -> olen, ?*nkaa -> ?*n kanssa
%
%Input: M\"{a} oon Tomminkaa
%Step 1: M\"{a} oon Tomminkaa
%        Min\"{a} oon Tomminkaa
%Step 2: M\"{a} oon Tomminkaa
%        Min\"{a} oon Tomminkaa
%        M\"{a} olen Tomminkaa
%        Min\"{a} olen Tomminkaa
%Step 3: M\"{a} oon Tomminkaa
%        Min\"{a} oon Tomminkaa
%        M\"{a} olen Tomminkaa
%        Min\"{a} olen Tomminkaa
%        M\"{a} oon Tommin kanssa
%        Min\"{a} oon Tommin kanssa
%        M\"{a} olen Tommin kanssa
%        Min\"{a} olen Tommin kanssa
%Rank:
%	-13.4885 ← min\"{a} olen Tommin kanssa
%	-12.7176 ← min\"{a} oon Tommin kanssa
%	-12.4408 ← m\"{a} olen Tommin kanssa
%	-9.2045 ← m\"{a} oon Tommin kanssa
%	-8.8651 ← min\"{a} olen Tomminkaa
%	-8.0941 ← min\"{a} oon Tomminkaa
%	-7.8174 ← m\"{a} olen Tomminkaa
%	-4.5811 ← m\"{a} oon Tomminkaa
%Output: Min\"{a} olen Tommin kanssa

>>>>

\begin{table*}
  \centering
  \begin{tabular}{|lrl|l|}
    \hline
    \textbf{Rules:} & & 1. m\"{a} $\rightarrow$ min\"{a} \\
     ~              & & 2. oon $\rightarrow$ olen \\
     ~              & & 3. (?+)nkaa $\rightarrow$ ...n kanssa \\
    \hline
  \end{tabular}
~\\
~\\
  \begin{tabular}{|l|r|l|l|}
    \hline
    \textbf{Input:} & \multicolumn{3}{l|}{M\"{a} oon Inarinkaa `I am with Inari'.} \\
    \hline
    \multirow{2}{*}{Step 1} & & M\"{a} oon Inarinkaa & apply rule 1 \\
                            & & Min\"{a} oon Inarinkaa & \\
    \hline
    \multirow{2}{*}{Step 2} & & M\"{a} oon Inarinkaa & apply rule 2 \\
                            &   & Min\"{a} oon Inarinkaa & \\
                            &   & M\"{a} olen Inarinkaa & \\
                            &   & Min\"{a} olen Inarinkaa & \\
    \hline
    \multirow{2}{*}{Step 3} &   & M\"{a} oon Inarinkaa   & apply rule 3\\
                            &   & Min\"{a} oon Inarinkaa  &\\
                            &   & M\"{a} olen Inarinkaa  &\\
                            &   & Min\"{a} olen Inarinkaa  &\\
                            &   & M\"{a} oon Inarin kanssa  &\\
                            &   & Min\"{a} oon Inarin kanssa  &\\
                            &   & M\"{a} olen Inarin kanssa  &\\
                            &   & Min\"{a} olen Inarin kanssa  &\\
    \hline
    \multirow{2}{*}{Step 4} & -4.5811 &  Min\"{a} olen Inarin kanssa & rank candidates \\
                            & -7.8174 &  Min\"{a} oon Inarin kanssa & \\
                            & -8.0941 &  M\"{a} olen Inarin kanssa & \\
                            & -8.8651&  M\"{a} oon Inarin kanssa & \\
                            & -9.2045 &  Min\"{a} olen Inarinkaa & \\
                            & -12.4408 &  Min\"{a} oon Inarinkaa & \\
                            & -12.7176 &  M\"{a} olen Inarinkaa & \\
                            & -13.4885 &  M\"{a} oon Inarinkaa & \\

    \hline
    \textbf{Output:} & \multicolumn{3}{l|}{Min\"{a} olen Inarin kanssa} \\
    \hline
  \end{tabular}
  \caption{Example trace of the unsupervised normalisation method. Rules are applied in order to each of 
     the possible candidate translations in turn. The candidates are then ranked using an $n$-gram language model 
     of standard Finnish and either an $n$-best list
     or the best candidate is output.}
  \label{table:unsup-trace}
\end{table*}
